\chapter{Current State of Design and Implementation}
This chapter presents the current state of design and implementation of the project. 

\section{Missing Topics}
There is a number of relevant topics, which were not presented in the previous chapters. These topics are roughly outlined here and will be incorporated into the previous chapters in the future.
\begin{description}
    \item[Game Engines as Visualization frameworks] Game engines such as Unreal Engine or Unity can be used as data visualization frameworks, and therefore should be mentioned in the section \ref{sec:frameworks}.
    \item[Graphic Libraries] A number of projects listed in chapter \ref{chapter:solutions} use graphic libraries such as OpenGL, WebGL, etc. To keep the list in the previous chapter complete, these libraries should be listed there as well.
    \item[Visual Programming] Visual programming langages are relevant topic and have yet not been described in the thesis. As the design of the project relies on the visual programming principles, it would be suitable to include an intro to the subject.
    \item[Printing 3D Models and Lego] The physical models have been presented in the previous chapter, however there is no section concerning the actual creation of the printed/assembled models.  
\end{description}

%review the requirements
\section{Design}
The project is being developed in cooperation with IPR Prague. Based on the previous research and consultations, the following specification of the visualization system has been proposed:
\begin{itemize}
    \item the system supports web-based presentation
    \item the system produces outputs which are needed for assembling or printing physical models  
    \item the system enables projection mapping the visualization onto physical models
    \item it is possible to process the urban data and style the visualization in an editor which is part of the system
    \item the system allows adding new functionalities
\end{itemize}




%present metacity demo

%present the python electron combo


